The semantic drift of quotations in blogspace: a case study in short-term cultural evolution

### 2016-08-06 reviews/2016-07-response-to-reviewers.tex

\title{Manuscript CS15-80\medskip\\
{\Large\em``The semantic drift of quotations in blogspace: a case study in short-term cultural evolution''}
\bigskip\\Response to Reviewers
}
\author{Sébastien Lerique and Camille Roth}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\makeatletter
\renewcommand{\subsection}{\clearpage\@startsection{section}{1}{0mm}
{\baselineskip}{\baselineskip\medskip\hrule\medskip}{\raggedright\Large\bf~\textcolor{MidnightBlue}}}
\makeatother

\newcommand{\critique}[1]{\begin{quote}#1\end{quote}}
\newcommand{\answer}[1]{{\setlength{\parindent}{0pt}\par\color{blue} #1}}
\newcommand{\answerok}[1]{{\setlength{\parindent}{0pt}\par\color{MidnightBlue} #1}}

@@

\medskip
We enclose an extensively revised version of the manuscript CS15-80 (initially titled ``How do we copy and paste? The semantic drift of quotations in blogspace'') based on the report you sent us on Jul 18, 2015.

\medskip
We hope that we have appropriately addressed the detailed remarks and very constructive questions made by you and the referees: to this effect, we also provide below a detailed response to each of these comments.  We additionally used a different color to emphasize the portions which were thoroughly rewritten.

\medskip
This comprehensive revision work led to a significantly longer manuscript than was originally submitted --- from around 6,300 words to about 9,000 words now, making it closer to a ``regular article'' than a ``brief report'': we hope that this will not be problematic at this stage.

\medskip
We look forward to reading your feedback on this new manuscript and apologize in advance for this long revision round.

@@

\critique{\itx{
\x what happens when you run a multi-factor regression model? Do the features interact?
\x clarify from the beginning the predictions you are making so that the results will be interpretable 
}}

\answer{Point to the regression model we introduced.}

\critique{Some low-level points:\itx{
\x the in vitro/in vivo distinction is unfamiliar and ought to be defined in the text
}
}

\answerok{In light of this potential unfamiliarity, we preferred to entirely avoid referring explicitly to this dichotomy (for instance, we now speak of ``corpus-based utterances'' instead of ``in vivo'').}

### 2016-08-06 brainscopycut.tex
minor before leaving

\title{The semantic drift of quotations in blogspace: a case study in short-term cultural evolution}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}
\abstract{
\newtext{We present a case study which connects psycholinguistics with the field of cultural evolution, in order to test for the existence of cultural attractors in the evolution of quotations.
Such attractors have been \tb{proposed} as \tb{a concept useful for} understanding cultural evolution %and its reciprocal influences 
\tb{in relation} with \tb{individual} cognition, but their existence has been hard to test.
\tb{We empirically} focus on \tb{the online transformation of} quotations when they are copied from blog to blog or media website: by coding words with a number of well-studied lexical features, we show that the way words are substituted in quotations is consistent (1) with the hypothesis of cultural attractors, and (2) with known effects of the word features.
In particular, words known to be harder to recall in lists have a higher tendency to be substituted, and words easier to recall are produced instead.
Our results support the hypothesis that cultural attractors can \tb{result} from the combination of individual cognitive biases in the interpretation and reproduction of representations.}
}
\authornote{Correspondence should be directed to lerique@cmb.hu-berlin.de and roth@cmb.hu-berlin.de}
\keywords{\newtext{word recall}; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; \emph{in vivo} psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}

>>>>

\title{The semantic drift of quotations in blogspace: a case study in short-term cultural evolution}
\shorttitle{The semantic drift of quotations in blogspace}
\date{}
\twoauthors{Sébastien Lerique}{Camille Roth}
\twoaffiliations{Centre d'Analyse et de Mathématique Sociales, UMR 8557 CNRS/EHESS\\190 av. de France, F-75013 Paris\\and Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}{CNRS\\Centre Marc Bloch Berlin, UMIFRE 14 CNRS/MAEE/HU\\Friedrichstr. 191, D-10117 Berlin}
\abstract{
\newtext{We present a case study which connects psycholinguistics with the field of cultural evolution, in order to test for the existence of cultural attractors in the evolution of quotations.
Such attractors have been \tb{proposed} as \tb{a concept useful for} understanding cultural evolution %and its reciprocal influences 
\tb{in relation} with \tb{individual} cognition, but their existence has been hard to test.
\tb{We empirically} focus on \tb{the online transformation of} quotations when they are copied from blog to blog or media website: by coding words with a number of well-studied lexical features, we show that the way words are substituted in quotations is consistent (1) with the hypothesis of cultural attractors, and (2) with known effects of the word features.
In particular, words known to be harder to recall in lists have a higher tendency to be substituted, and words easier to recall are produced instead.
Our results support the hypothesis that cultural attractors can \tb{result} from the combination of individual cognitive biases in the interpretation and reproduction of representations.}
}
\authornote{Correspondence should be directed to lerique@cmb.hu-berlin.de and roth@cmb.hu-berlin.de}
\keywords{\newtext{word recall}; recollection bias; semantic network; cultural evolution; cultural attraction; data mining; big data; psycholinguistics}
%\note{\TB{Note XXXX (version? date?)}}
